%\documentclass[12pt]{report} %,twoside
%\usepackage{kjfsty}
%\begin{document}
%\onehalfspacing
%\frenchspacing

\chapter*{Conference Presentations}
\renewcommand{\chaptermark}[1]{%
\markboth{\normalfont \textbf{\textsl{#1}}}{}}
\markboth{Conference Presentations}{Conference Presentations}


\addcontentsline{toc}{chapter}{Conference Presentations}
\chaptermark{Conference Presentations}

\begin{list}{}{
  \setlength{\leftmargin}{0.25in}
  \setlength{\rightmargin}{0.25in}
  \setlength{\itemsep}{6pt}
}
\item \textbf{K.~J.~Franz}, K.-T. Shiu, S. R. Forrest, and C.~Gmachl, ``A dual-wavelength quantum cascade laser with two optical transitions in each active region,'' \emph{IPRM}  Princeton, NJ, May 2006. \enspace \tb{Best Student Paper Award}
\item \textbf{K.~J.~Franz}, K.-T. Shiu, S. R. Forrest, and C.~Gmachl, ``Excited state and dual-wavelength quantum cascade lasers,'' \emph{CLEO Semiconductor Laser Workshop}  Long Beach, CA, June 2006.
\item A. Shen, H. Lu, M.~C.~Tamargo, W. Charles, I. Yokomizo, C. Y. Song, H.~C.~Liu,  S. K. Zhang, X. Zhou, R. R. Alfano, \textbf{K.~J.~Franz}, and C.~Gmachl, ``Intersubband Transitions in MBE-grown Wide Bandgap II--VI Semiconductors,'' \emph{NAMBE}~ Durham, NC, Oct 2006.
\item S. Zhang, X. Zhou, A. Shen, W. Wang, R. Alfano, H. Lu, W. O. Charles, I. Yokomizo, M.~C.~Tamargo, \textbf{K.~J.~Franz}, and C.~Gmachl, ``Optical Properties of Heavily Doped n-type CdSe Quantum Dots for Intersubband Device Applications,'' \emph{MRS Fall Meeting}~ Boston, MA, Nov 2006.
\item \textbf{K.~J.~Franz}, K.-T. Shiu, S. R. Forrest, and C.~Gmachl, ``Monolithic Mid-Infrared  Integration of a Quantum Cascade Laser and a Passive Semiconductor Waveguide,'' \emph{APS March Meeting}~ Denver, CO, Mar 2007.
\item \textbf{K.~J.~Franz}, D. Wasserman, A. J. Hoffman, K.-T. Shiu, S. R. Forrest, and C.~Gmachl, ``Cascaded Emission in a Dual-Wavelength Quantum Cascade Laser,''  \emph{PRISM/PCCM/MIRTHE Industry Day}~ Princeton, NJ, Mar 2007.
\item \textbf{K.~J.~Franz}, D. Wasserman, A. J. Hoffman, K.-T. Shiu, S. R. Forrest, and C.~Gmachl, ``Cascaded Emission in a Dual-Wavelength Quantum Cascade Laser,'' \emph{CLEO}~  Baltimore, MD, May 2007.
\item S.~S.~Howard, A. J. Hoffman, \textbf{K.~J.~Franz}, T. Ko, and C.~Gmachl, ``Current Injection Transition Broadening in Quantum Cascade Lasers,'' \emph{ITQW} Ambleside, Cumbria, U.K., Sept 2007.
\item \textbf{K.~J.~Franz}, S. Menzel, A. J. Hoffman, D. Wasserman, K.-T. Shiu, S. R. Forrest, and C.~Gmachl, ``Excited State Optical Transitions in Quantum Cascade Lasers for Low Thresholds and Multi-Wavelength Emission,'' \emph{ITQW} Ambleside, Cumbria, U.K., Sept 2007.
\item W. O. Charles, A. Shen, \textbf{K.~J.~Franz}, C.~Gmachl, Q. Zhang, Y. Gong, G. F. Neumark, and M.~C.~Tamargo, ``Asymmetric Coupled Quantum Well Structure for Quantum Cascade Laser Applications,'' \emph{NAMBE}~ Albuquerque, NM, Sept 2007.
\item A. J. Hoffman, S. Schartner, S.~S.~Howard, \textbf{K.~J.~Franz}, F. Towner, and C.~Gmachl, ``Low-Voltage Defect Quantum Cascade Laser with Heterogeneous Injector  Regions,'' \emph{IEEE LEOS Annual Meeting}~ Lake Buena Vista, FL, Oct 2007.
\item S.~S.~Howard, A. J. Hoffman, \textbf{K.~J.~Franz}, D. P. Howard, T. Ko, D. L. Sivco, and  C.~F.~Gmachl, ``Effect of Injection Barrier Thickness and Doping on Transport and Gain in a $\lambda=8.2$~\um\ Quantum Cascade Laser,'' \emph{IEEE LEOS Annual Meeting}  Lake Buena Vista, FL, Oct 2007.
\item \textbf{K.~J.~Franz}, A. J. Hoffman, S.~S.~Howard, Z. J. Liu, S. Menzel, S. Schartner,  D. Wasserman, and C.~Gmachl, ``Mid-Infrared Quantum Cascade Lasers,''  \emph{Mauterndorf Winterschool}~ Bad Hofgastein, Austria, Feb 2008.
\item \textbf{K.~J.~Franz}, S. Menzel, A. J. Hoffman, D. Wasserman, J. W. Cockburn, and  C.~Gmachl, ``High \emph{k}-Space Lasing in a Dual Optical Transition Quantum Cascade Laser,'' \emph{Mauterndorf Winterschool}~ Bad Hofgastein, Austria, Feb 2008.  poster presentation
\item \textbf{K.~J.~Franz}, S. Menzel, A. J. Hoffman, D. Wasserman, J. W. Cockburn, and  C.~Gmachl, ``Excited State Quantum Cascade Lasers and Lasing in \emph{k}-Space,''  \emph{PRISM/PCCM/MIRTHE Industry Day}~ Princeton, NJ, Mar 2008.
\item M. D. Escarra, A. J. Hoffman, S.~S.~Howard, \textbf{K.~J.~Franz}, A. Sridhar, and C.~Gmachl, ``High Efficiency Quantum Cascade Lasers,'' \emph{APS March Meeting}~ New Orleans, LA, Mar 2008.
\item W. O. Charles, \textbf{K.~J.~Franz}, A. Shen, M.~C.~Tamargo, and C.~Gmachl, ``Growth and properties of wide band gap II--VI multi-quantum well structures for mid-infrared quantum cascade lasers,'' \emph{APS March Meeting}~ New Orleans, LA, Mar 2008.
\item M. A. Talukder, F.-S. Choa, C. R. Menyuk, \textbf{K.~J.~Franz}, S.~S.~Howard, C.~F.~Gmachl ``Novel Heat Removal Waveguide Structure for High Performance Quantum  Cascade Lasers,'' \emph{CLEO}~ San Jose, CA, May 2008. poster presentation
\item A. J. Hoffman, S. Schartner, S.~S.~Howard, \textbf{K.~J.~Franz}, F. Towner, and C.~Gmachl, ``Low Voltage Defect Heterogeneous Quantum Cascade Laser,'' \emph{CLEO} San Jose, CA, May 2008.
\item S. Menzel, \textbf{K.~J.~Franz}, D. Wasserman, A. J. Hoffman, J. W. Cockburn, and  C.~F.~Gmachl, ``Laser Action at High \emph{k}-Space Values in Anti-Correlated  Multi-Wavelength Quantum Cascade Lasers,'' \emph{CLEO}~ San Jose, CA, May 2008.
\item \textbf{K.~J.~Franz}, W. O. Charles, A. Shen, A. J. Hoffman, M.~C.~Tamargo, and C.~Gmachl, ``Intersubband Electroluminescence from a ZnCdSe/ZnCdMgSe Quantum  Cascade Structure,'' \emph{CLEO}~ San Jose, CA, May 2008.
\item Y.~Dikmelik, J.~B.~Khurgin, A. J. Hoffman, S.~S.~Howard, \textbf{K.~J.~Franz}, and C.~F.~Gmachl, ``Excited-State Absorption in High-Power Mid-Infrared Quantum Cascade Lasers,'' \emph{CLEO}~ San Jose, CA, May 2008. poster presentation
\item \textbf{K.~J.~Franz}, W. O. Charles, A. Shen, A. J. Hoffman, M.~C.~Tamargo, and C.~Gmachl, ``Electroluminescence from a ZnCdSe/ZnCdMgSe Quantum Cascade Structure,'' \emph{ICPS}~ Rio de Janeiro, Brazil, July 2008.  poster presentation
\item \textbf{K.~J.~Franz}, S. Menzel, D. Wasserman, A. J. Hoffman, J. W. Cockburn, and C.~Gmachl, ``High \emph{k}-Space Lasing in Excited State Quantum Cascade Lasers,'' \emph{ICPS}  Rio de Janeiro, Brazil, July 2008.
\item A. Shen, W. O. Charles, B. S. Li, \textbf{K.~J.~Franz}, C.~Gmachl, Q. Zhang, and  M.~C.~Tamargo, ``Wide Band Gap II--Selenides for Short Wavelength Intersubband Devices,'' \emph{MBE2008} Vancouver, Canada, Aug 2008.
\item A. J. Hoffman, M. D. Escarra, S.~S.~Howard, \textbf{K.~J.~Franz}, X.~Wang, \mbox{J.-Y.~Fan}, and C.~Gmachl, ``Strategies for Improved Wall-plug Efficiency in Quantum Cascade Lasers,'' \emph{MIOMD IX}~ Freiburg, Germany, Sept 2008.
\item \textbf{K.~J.~Franz}, W. O. Charles, A. Shen, A. J. Hoffman, M.~C.~Tamargo, and C.~Gmachl, ``Quantum Cascade Electroluminescence from a ZnCdSe/ZnCdMgSe on InP  Structure,'' \emph{MIOMD IX}~ Freiburg, Germany, Sept 2008.
\item Y. Yao, Z. Liu, A. J. Hoffman, \textbf{K.~J.~Franz}, and C.~F.~Gmachl, ``Voltage tunability of quantum cascade lasers,'' \emph{IQCLSW}~ Monte Verita, Switzerland, Sept 2008.
\item Y.~Dikmelik, J.~B.~Khurgin, A. J. Hoffman, S.~S.~Howard, \textbf{K.~J.~Franz}, and C.~F.~Gmachl, ``Excited-State Absorption in High-Power Mid-Infrared Quantum Cascade Lasers,'' \emph{IQCLSW}~ Monte Verita, Switzerland, Sept 2008. poster presentation
\item M. D. Escarra, A. J. Hoffman, S.~S.~Howard, \textbf{K.~J.~Franz}, X.~Wang, M. Fong, and  C.~F.~Gmachl, ``Improved Voltage Efficiency in Quantum Cascade Lasers,''  \emph{IQCLSW}~ Monte Verita, Switzerland, Sept 2008. poster presentation
\item W. O. Charles, \textbf{K.~J.~Franz}, A. Shen, Q. Zhang, C.~Gmachl, and M.~C.~Tamargo, ``Growth and Characterization of Zn\sub{x}Cd\sub{1-x}Se / Zn\sub{x^\prime}Cd\sub{y^\prime}Mg\sub{1-x^\prime-y^\prime}Se Quantum Cascade Emitters,'' \emph{IQCLSW}~ Monte Verita, Switzerland, Sept 2008.
\item \textbf{K.~J.~Franz}, P. Q. Liu, A. J. Hoffman, S.~S.~Howard, M. D. Escarra, Y.~Dikmelik,  J.~B.~Khurgin, X.~Wang, \mbox{J.-Y.~Fan}, and C.~Gmachl, ``Short Injector Regions for  Improved Quantum Cascade Laser Performance,'' \emph{IQCLSW}~ Monte Verita,  Switzerland, Sept 2008. \enspace \tb{Invited}
\item Y. Yao, \textbf{K.~J.~Franz}, Z. Liu, A. J. Hoffman, and C.~F.~Gmachl, ``Voltage tuning of gain spectra in quantum cascade lasers,'' \emph{Photonics West}~ San Jose, CA, Feb 2009.
\item Y.~Dikmelik, J.~B.~Khurgin, M. D. Escarra, P. Q. Liu, A. J. Hoffman, \textbf{K.~J.~Franz}, C.~F.~Gmachl, \mbox{J.-Y.~Fan}, and W. Wang ``Intersubband Absorption Loss in High-Performance Mid-Infrared Quantum Cascade Lasers,'' \emph{CLEO}~ Baltimore, MD, June 2009. poster presentation
\item M. D. Escarra, A. J. Hoffman, \textbf{K.~J.~Franz}. S.~S.~Howard, X.~Wang, \mbox{J.-Y.~Fan}, and C.~Gmachl, ``Ultra-Low Voltage Defect Quantum Cascade Lasers,''  \emph{CLEO}~ Baltimore, MD, June 2009.
\item A. J. Hoffman, P. X. Braun, M. D. Escarra, S.~S.~Howard, \textbf{K.~J.~Franz}, X.~Wang, \mbox{J.-Y.~Fan}, C.~Gmachl, ``Instantaneous Power and Threshold in Continuous Wave Quantum Cascade Lasers,'' \emph{CLEO}~ Baltimore, MD, June 2009.
\item P. Q. Liu, A. J. Hoffman, M. D. Escarra, \textbf{K.~J.~Franz}, J.~B.~Khurgin, Y.~Dikmelik, X.~Wang, \mbox{J.-Y.~Fan}, and C.~F.~Gmachl, ``Quantum Cascade Lasers with Ultra-Strong Coupling Injection,'' \emph{CLEO}~ Baltimore, MD, June 2009.
\item \textbf{K.~J.~Franz}, J. J. J. Raftery, P. Q. Liu, A. J. Hoffman, M. D. Escarra, S.~S.~Howard, Y.~Dikmelik, J.~B.~Khurgin, X.~Wang, \mbox{J.-Y.~Fan}, and C.~Gmachl, ``Negative Differential Resistance and Pulse Instabilities in Minimalized Quantum Cascade Laser Structures,'' \emph{CLEO}~ Baltimore, MD, June 2009.
\item Y. Yao, \textbf{K.~J.~Franz}, X.~Wang, \mbox{J.-Y.~Fan}, and C.~F.~Gmachl, ``Widely Voltage Tunable Quantum Cascade Lasers,'' \emph{CLEO}~ Baltimore, MD, June 2009.
\item C. Young, R. Cendejas, S.~S.~Howard, W. Sanchez-Vaynshteyn, A. J. Hoffman, \textbf{K.~J.~Franz}, Y. Yao, G. Mizaikoff, X.~Wang, \mbox{J.-Y.~Fan}, and C.~F.~Gmachl, ``Enhancing Wavelength Selection for Quantum Cascade Laser Based Chemical Sensors by Cavity Length Variation,'' \emph{CLEO}~ Baltimore, MD, June 2009. poster presentation
\item J.~B.~Khurgin, Y.~Dikmelik, P. Q. Liu, A. J. Hoffman, M. D. Escarra, \textbf{K.~J.~Franz}, and C.~F.~Gmachl, ``Role of Interface Roughness in the Transport and Lasing Characteristics of Quantum-Cascade Lasers,'' \emph{CLEO}~ Baltimore, MD, June 2009.
%
\end{list}

%\end{document} 