%\documentclass[12pt]{report} %,twoside
%\usepackage{kjfsty}
%\begin{document}
%\onehalfspacing
%\frenchspacing


\chapter*{Publications}
\renewcommand{\chaptermark}[1]{%
\markboth{\normalfont \textbf{\textsl{#1}}}{}}

\addcontentsline{toc}{chapter}{Publications}
\chaptermark{Publications}



\begin{list}{}{
  \setlength{\leftmargin}{0.25in}
  \setlength{\rightmargin}{0.25in}
  \setlength{\itemsep}{6pt}
}
\item \textbf{K. J. Franz}, K.-T. Shiu, S. R. Forrest, and C. Gmachl, ``A dual-wavelength quantum cascade laser with two optical transitions in each active region,'' \emph{Proc. IPRM}~ \tb{18}, 26 (2006).
\item H. Lu, A. Shen, W. Charles, I. Yokomizo, M. C. Tarmargo, \textbf{K. J. Franz}, C. Gmachl, and M. Munoz, ``Optical characterization of intersubband transitions in \linebreak Zn\sub{x}Cd\sub{1-x}Se / Zn\sub{x^\prime}Cd\sub{y^\prime}Mg\sub{1-x^\prime-y^\prime}Se multiple quantum well structures by contact-less electroreflectance,'' \emph{Appl. Phys. Lett.}~ \tb{89}, 241921 (2006).
\item S. Zhang, X. Zhou, A. Shen, W. Wang, R. Alfano, H. Lu, W. O. Charles, I. Yokomizo, M. C. Tamargo, \textbf{K. J. Franz}, and C. Gmachl, ``Optical Properties of Heavily Doped  n-type CdSe Quantum Dots for Intersubband Device Applications,'' \emph{Proc. MRS}~ \linebreak \tb{959E}, 0959-M06-05 (2006).
\item A. Shen, H. Lu, M. C. Tamargo, W. Charles, I. Yokomizo, \textbf{K. J. Franz}, C. Gmachl, S. K. Zhang, X. Zhou, R. R. Alfano, and H. C. Liu, ``Intersubband absorption in CdSe/ZnCdMgSe self-assembled quantum dot multi-layers,'' \emph{Appl. Phys. Lett.}~ \tb{90}, 071910 (2007).
\item \textbf{K. J. Franz}, D. Wasserman, A. J. Hoffman, D.C. Jangraw, K.-T. Shiu, S. R. Forest, and C. Gmachl, ``Evidence of cascaded emission in a dual-wavelength Quantum Cascade laser,'' \emph{Appl. Phys. Lett.}~ \tb{90}, 091104 (2007).
\item A. Shen, H. Lu, M. C. Tamargo, W. Charles, I. Yokomizo, C. Y. Song, H. C. Liu,  \linebreak S. K. Zhang, X. Zhou, R. R. Alfano, \textbf{K. J. Franz}, and C. Gmachl, ``Intersubband transitions in molecular-beam-epitaxy-grown wide band gap II--VI semiconductors,'' \emph{J. Vac. Sci. Tech. B}~ \tb{25}, 995 (2007).
\item H. Lu, A. Shen, M. C. Tamargo, W. Charles, I. Yokomizo, M. Munoz, Y. Gong, \linebreak G. F. Neumark, \textbf{K. J. Franz}, C. Gmachl, C. Y. Song, and H.C. Liu, ``Study of intersubband transitions of Zn\sub{x}Cd\sub{1-x}Se/Zn\sub{x}Cd\sub{y}Mg\sub{1-x-y}Se multiple quantum wells grown by molecular beam epitaxy for midinfrared device applications,'' \linebreak \emph{J. Vac. Sci. Tech. B}~ \tb{25}, 1103 (2007).
\item A. J. Hoffman, L. Alekseyev, S. S. Howard, \textbf{K. J. Franz}, D. Wasserman, \linebreak V. A. Podolskiy, E. E. Narimanov, D. L. Sivco, and C. Gmachl, ``Negative refraction in semiconductor metamaterials,'' \emph{Nature Materials}~ \tb{6}, 946 (2007).
\item A. J. Hoffman, S. Schartner, S. S. Howard, \textbf{K. J. Franz}, F. Towner, and C. Gmachl, ``Low voltage-defect quantum cascade laser with heterogeneous injector regions,'' \emph{Opt. Express}~ \tb{15}, 15818 (2007).
\item \textbf{K. J. Franz}, W. O. Charles, A. Shen, A. J. Hoffman, M. C. Tamargo, and C. Gmachl, ``ZnCdSe/ZnCdMgSe Quantum Cascade Electroluminescence,'' \emph{Appl. Phys. Lett.}~  \linebreak \tb{92}, 121105 (2008).
\item W. O. Charles, A. Shen, \textbf{K. J. Franz}, C. Gmachl, Q. Zhang, Y. Gong, G. F. Neumark, and M. C. Tamargo, ``Growth and Characterization of Zn\sub{x}Cd\sub{1-x}Se / \linebreak Zn\sub{x^\prime}Cd\sub{y^\prime}Mg\sub{1-x^\prime-y^\prime}Se Asymmetric Coupled Quantum Well Structures for Quantum Cascade Laser Applications,'' \emph{J. Vac. Sci. Tech. B}~ \tb{26}, 1171 (2008).
\item A. Shen, W. O. Charles, B. S. Li, \textbf{K. J. Franz}, C. Gmachl, Q. Zhang, and M. C. Tamargo, ``Wide Band Gap II--VI Selenides for Short Wavelength Intersubband Devices,''  \linebreak \emph{J. Cryst. Growth}, doi:10.1016/j.jcrysgro.2008.10.102.
\item W. O. Charles, \textbf{K. J. Franz}, A. Shen, A. Zhang, B. Li, Y Gong, G. F. Neumark,  \linebreak C. Gmachl, and M. C. Tamargo, ``Molecular Beam Epitaxy Growth of Zn\sub{x}Cd\sub{1-x}Se / Zn\sub{x^\prime}Cd\sub{y^\prime}Mg\sub{1-x^\prime-y^\prime}Se---InP Quantum Cascade Structures,'' \emph{J. Cryst. Growth}~ \tb{310}, 5380 (2008).
\pagebreak
\item S. S. Howard, D. P. Howard, \textbf{K. J. Franz}, A. J. Hoffman, D. L. Sivco, and C. Gmachl, ``The effect of injector barrier thickness and doping level on current transport and optical transition width in a $\lambda\sim8$~\um\ QC structure,'' \emph{Appl. Phys. Lett.}~ \tb{93}, 191107 (2008).
\item  \textbf{K. J. Franz}, S. Menzel, A. J. Hoffman, D. Wasserman, J. W. Cockburn, and \linebreak C. Gmachl, ``High \emph{k}-space lasing in a dual wavelength quantum cascade laser,''  \emph{Nature Photonics}~ \tb{3}, 50 (2008).
\item Y. Yao, \textbf{K. J. Franz}, Z. Liu, A. J. Hoffman, and C. F. Gmachl, ``Voltage tuning of gain spectra in quantum cascade lasers,'' \emph{Proc. SPIE}~ \tb{7230}, 723012 (2009).
\item A. J. Hoffman, P. X. Braun, M. D. Escarra, \textbf{K. J. Franz}, X. Wang, and C. Gmachl, ``Lasing-induced reduction of core heating in high wall plug efficiency quantum cascade lasers,'' \emph{Appl. Phys. Lett.}~ \tb{94}, 041101 (2009).
\item J. B. Khurgin, Y. Dikmelik, P. Q. Liu, A. J. Hoffman, M. D. Escarra, \textbf{K. J. Franz}, \linebreak and C. F. Gmachl, ``Role of interface roughness in the transport and lasing characteristics of quantum-cascade lasers,'' \emph{Appl. Phys. Lett.}~ \tb{94}, 091101 (2009).
\item C. R. Young, R. Cendejas, S. S. Howard, W. Sanchez-Vaynshteyn, A. J. Hoffman,  \linebreak \textbf{K. J. Franz}, Y. Yao, B. Mizaikoff, X. Wang, J.-Y. Fan, and C. Gmachl, ``Wavelength \linebreak selection for quantum cascade lasers by cavity length,'' \emph{Appl. Phys. Lett.}~ \tb{94}, \linebreak 091109 (2009).
\item Y. Yao, Z. J. Liu, A. J. Hoffman, \textbf{K. J. Franz}, and C. F. Gmachl, ``Voltage Tunability of Quantum Cascade Lasers,'' \emph{IEEE J. Quantum Electron.}, accepted.
\item A. J. Hoffman, L. Alekseyev, A. Sridhar, P. X. Braun, S. S. Howard, \textbf{K. J. Franz},  \linebreak D. Wasserman, V. A. Podolskiy, E. E. Narimanov, D. L. Sivco, and C. Gmachl, ``Mid-infrared Semiconductor Optical Metamaterials,'' \emph{J. Appl. Phys.}, accepted.
\item \textbf{K. J. Franz}, M. D. Escarra, A. J. Hoffman, P. Q. Liu, J. J. J. Raftery, S. S. Howard,  \linebreak Y. Dikmelik, J. B. Khurgin, X. Wang, J.-Y. Fan, C. Gmachl, ``Short Injector Quantum Cascade Lasers,'' \emph{IEEE J. Quantum Electron.}, submitted.
\item M. D. Escarra, A. J. Hoffman, \textbf{K. J. Franz}, S. S. Howard, R. Cendejas, X. Wang, J.-Y. Fan, and C. Gmachl, ``Voltage defect in quantum cascade lasers of less than one longitudinal optical phonon energy,'' \emph{Appl. Phys. Lett.}, submitted.
\item Y. Yao, \textbf{K. J. Franz}, X. Wang, J.-Y. Fan, and C. Gmachl, ``Widely voltage tunable gain spectra of quantum cascade lasers,'' \emph{Appl. Phys. Lett.}, submitted.
\item P. Q. Liu, A. J. Hoffman, M. D. Escarra, \textbf{K. J. Franz}, J. B. Khurgin, Y. Dikmelik, X. Wang, J.-Y. Fan, and C. Gmachl, ``Highly Power-Efficient Mid-Infrared Lasers,'' \emph{Science}, submitted.
\end{list}



%\end{document} 